Analysis

### 2023-02-27 analysis/analysis.Rmd
update figures and analysis scripts

---
title: "Analysis"
author: "Andrew Morris"
date: "2022-11-21"
output: 
    html_document:
        toc: true
editor_options: 
  chunk_output_type: console
---

@@

```{r initialize_packages, message=FALSE}
library(morris)
library(broom)
library(knitr)
library(broman)
library(phyloseq)
library(knitr)
library(magrittr)
library(vegan)
library(ggpubr)
library(ggtext)
library(ALDEx2)
library(corncob)
library(ANCOMBC)
library(tidyverse)
library(here)
library(patchwork)

@@

set.seed(1337)
```

@@

ggplot(fluxes, aes(x = passage, y = ch4, color = treat)) +
    stat_smooth(method = 'lm', se = FALSE, formula = 'y ~ x') +
    scale_color_manual(
        name = "Treatment", 
        labels = c('Neutral', 'Positive'), 
        values = c('gray40', 'darkorange2')) +
    geom_jitter(width = 0.1) + 
    labs(x = "Passage Number", 
         y = "Methane Oxidation Rate (-k)") +
  scale_x_continuous(labels = 1:5)
```

@@

(p_response <- ggplot(fluxes, aes(x = passage, y = log_ch4, color = treat)) +
    stat_smooth(method = 'lm', se = FALSE, formula = 'y ~ x') +
    scale_color_manual(
      name = "Treatment", 
      labels = c('Neutral', 'Positive'), 
      values = c('gray40', 'darkorange2')) +
    geom_jitter(#aes(alpha = selected), 
      width = 0.1) + 
        labs(x = "Passage Number", 
                  y = expression(log[10] ~ CH[4] ~ "(-k)")) +
  scale_x_continuous(labels = 1:5) +
    coord_fixed(ratio))

@@

# ggsave(here(fig_dir, 'fig1.jpg'), p_response, width = 4, height = 3)
# ggsave(here(fig_dir, 'fig1.svg'), p_response, width = 4, height = 3)

@@

ratio_div <- calc_plot_ratios(divergence$passage, divergence$divergence)
(
p_div <-
ggplot(divergence, 
       aes(x = passage, 
           y = divergence)) +
    stat_smooth(method = 'lm', 
                se = FALSE, 
                formula = 'y ~ x',
                color = "black",
                linewidth = 0.5) +
    geom_point() + 
    labs(x = expression(atop("Passage Number", " ")), 
         y = expression(atop("Divergence", log[10] ~ CH[4] ~ "(-k)"))) +
    coord_fixed(ratio_div) +
    scale_x_continuous(labels = 1:5) + 
    scale_y_continuous(n.breaks = 4) +
    theme(plot.margin = margin(0, 0.25, 0, 0.5, "cm"))
)
ratio_rh <- calc_plot_ratios(rh$sd_csum, rh$divergence)

(
p_rh <-
rh %>% 
ggplot(aes(x = sd_csum, 
           y = divergence)) +
    stat_smooth(method = 'lm',
                se = F,
                formula = 'y ~ x',
                color = "black",
                linewidth = 0.5) +
    geom_point() + 
    labs(x = expression(atop("Cumulative Selection Differential", log[10] ~ CH[4] ~ "(-k)")), 
         y = expression(atop("Divergence", log[10] ~ CH[4] ~ "(-k)"))) +
    scale_y_continuous(n.breaks = 4) +
    # theme(plot.margin = margin(0, 0.5, 0, 0.25, "cm")) +
    coord_fixed()
)

@@

# ggsave(here(fig_dir, "fig2.png"), width = 8*.9, height = 4*.9)
# ggsave(here(fig_dir, "fig2.svg"), width = 8*.9, height = 4*.9)

# save(rh_model, file = here(der_dir, 'herit_model.RData'))

@@

centroids <-
  nmds_data %>% 
  group_by(passage, treat) %>% 
  summarize(NMDS1 = mean(NMDS1),
            NMDS2 = mean(NMDS2),
            .groups = "drop")
p_beta <-
  nmds_data %>%   
  ggplot(aes(x = NMDS1, y = NMDS2, shape = passage, color = treat)) +
  geom_point() +
  stat_ellipse(show.legend = FALSE) +
  coord_fixed() +
  scale_shape_discrete(name = "Passage", labels = c(2, 5)) +
  scale_color_manual(name = "Treatment",
                       labels = c('Neutral', 'Positive'),
                       values = c('gray40', 'darkorange2')) #+
  # theme_bw() +
  # theme(
  #   plot.background = element_blank(),
  #   panel.grid.major = element_blank(),
  #   panel.grid.minor = element_blank())
  #   
pcoa <- cmdscale(rare_dist_bray, eig = TRUE, add = TRUE)
round(pcoa$eig*100/sum(pcoa$eig),1)
pcoa_per_exp <- 100 * eigenvals(pcoa) / sum(eigenvals(pcoa))

ratio = pcoa_per_exp[2]/pcoa_per_exp[1]

pcoa_scores <-
  scores(pcoa, display = "sites") %>% 
  as_tibble(rownames = "sample")

pcoa_data <-
  aes_data %>% 
  select(sample, passage, treat) %>% 
  distinct %>% 
  inner_join(pcoa_scores, by = "sample")
# p_beta <-
  pcoa_data %>%   
  ggplot(aes(x = Dim1, y = Dim2, shape = passage, color = treat)) +
  geom_point() +
  stat_ellipse(show.legend = FALSE) +
  coord_fixed(ratio) +
  scale_shape_discrete(name = "Passage", labels = c(2, 5)) +
  scale_color_manual(name = "Treatment",
                       labels = c('Neutral', 'Positive'),
                       values = c('gray40', 'darkorange2')) #+
  # theme_bw() +
  # theme(
  #   plot.background = element_blank(),
  #   panel.grid.major = element_blank(),
  #   panel.grid.minor = element_blank())

@@

# ggsave(here(fig_dir, 'fig3.png'), p_beta, height = 2.5, width = 4) 
# ggsave(here(fig_dir, 'fig3.svg'), p_beta, height = 2.5, width = 4)

@@

all_taxa$Family <- factor(all_taxa$Family, levels = sort_order$Family)
all_iqm$Family <- factor(all_iqm$Family, levels = sort_order$Family)
all_taxa <-
  all_taxa %>% 
  mutate(direction = if_else(effect > 0, 0, 1))
all_iqm <-
all_taxa %>% 
  select(Family, direction) %>% 
  distinct() %>% 
  full_join(all_iqm, by = "Family")
(p <-
	all_taxa %>%
	ggplot(aes(x = rel_abund, y = Family, color = treat)) +
	geom_point(position=position_jitterdodge()) +
	geom_pointrange(aes(x = median, xmax = third_quartile, xmin = first_quartile, fill = treat), 
			data = all_iqm, 
			position = position_dodge(width = 0.75), 
			shape = 21, 
			color = "black") +
	theme_bw() +
	theme(axis.text.y = element_markdown()) +
	labs(x = "Relative Abundance (%)", y = NULL) +
	scale_color_manual(name = "Treatment",
			   labels = c('Neutral', 'Positive'),
			   values = c('gray40', 'darkorange2')) +
	scale_fill_manual(name = "Treatment",
			   labels = c('Neutral', 'Positive'),
			   values = c('gray40', 'darkorange2')) +
    facet_grid(direction ~ ., scale = "free_y", space = "free")  + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank()
))

(p_log10 <- 
	p +
	scale_x_log10(breaks = c(0.001, 0.01, 0.1, 1),
		      labels = c(0.001, 0.01, 0.1, 1)))

@@

# ggsave(here(fig_dir, 'fig4.jpg'), p_log10, width = 5, height = 5) 
# ggsave(here(fig_dir, 'fig4.svg'), p_log10, width = 5, height = 5)

@@

p_effect <-
	all_taxa %>%
	ggplot(aes(x = effect, y = Family)) +
	geom_point() +

	theme_bw() +
	theme(axis.text.y = element_markdown()) +
	labs(x = "Aldex2 Effect Size", y = NULL) +
	scale_color_manual(name = "Treatment",
			   labels = c('Neutral', 'Positive'),
			   values = c('gray40', 'darkorange2')) +
	scale_fill_manual(name = "Treatment",
			   labels = c('Neutral', 'Positive'),
			   values = c('gray40', 'darkorange2'))
p_effect

@@

save(p_response, herit_plot, p_beta, p_log10, file = here(der_dir, 'plots.RData'))
save(response_model, compare_response_mods, per_slope, rh_model, kt, wt, rare_median, s5, min_seqs, tidy_permanova, dbrda_aov, dbrda_percent_explained, da_fams, file = here(der_dir, 'models.RData'))

>>>>

---
title: "Analysis"
author: "Andrew Morris"
date: "`r Sys.Date()`"
output: 
    html_document:
        toc: true
editor_options: 
  chunk_output_type: console
---

@@

```{r initialize_packages, message=FALSE}
library(morris)
library(broom)
library(knitr)
library(broman)
library(phyloseq)
library(knitr)
library(magrittr)
library(vegan)
library(ggpubr)
library(ggtext)
library(ALDEx2)
library(corncob)
library(ANCOMBC)
library(tidyverse)
library(here)
library(patchwork)
library(extrafont)

@@

set.seed(1337)

theme_set(theme_classic(base_size = 7) +
            theme(panel.border = element_rect(fill = NA, linewidth = 1.0625),
                  axis.line = element_blank(),
                  text = element_text(family = 'Arial')))
```

@@

ggplot(fluxes, aes(x = passage, y = ch4, color = treat)) +
    stat_smooth(method = 'lm', se = FALSE, formula = 'y ~ x') +
    scale_color_manual(
        name = "Treatment", 
        labels = c('Control', 'Selection'), 
        values = c('gray40', 'darkorange2')) +
    geom_jitter(width = 0.1) + 
    labs(x = "Passage Number", 
         y = "Methane Oxidation Rate (-k)") +
  scale_x_continuous(labels = 1:5)
```

@@

# (p_response_cl <- ggplot(fluxes, aes(x = passage, y = log_ch4, color = treat)) +
#     stat_smooth(method = 'lm', se = FALSE, formula = 'y ~ x') +
#     scale_color_manual(
#       name = "Treatment", 
#       labels = c('Control', 'Selection'), 
#       values = c('gray40', 'darkorange2')) +
#     geom_jitter(#aes(alpha = selected), 
#       width = 0.1) + 
#         labs(x = "Passage Number", 
#                   y = expression(log[10] ~ CH[4] ~ "(-k)")) +
#   scale_x_continuous(labels = 1:5) +
#     coord_fixed(ratio))

@@

# ggsave(here(fig_dir, 'fig2.jpg'), p_response, width = 4, height = 3)
# ggsave(here(fig_dir, 'fig2.svg'), p_response, width = 4, height = 3)
# ggsave(here(fig_dir, 'fig2_cl.png'), p_response_cl, width = 4, height = 3)

(p_response_bw <- ggplot(fluxes, aes(x = passage, y = log_ch4, fill = treat, linetype = treat)) +
    stat_smooth(method = 'lm', se = FALSE, formula = 'y ~ x', color = 'black',
                linewidth = 0.5) +
    scale_fill_manual(
      name = "Treatment", 
      labels = c('Control', 'Selection'), 
      values = c('white', 'black')) +
    scale_linetype_manual(
      name = "Treatment", 
      labels = c('Control', 'Selection'), 
      values = c(3, 1)) +
        geom_jitter(shape = 21, 
      width = 0.1,
      size = 1) + 
        labs(x = "Passage Number", 
                  y = expression(log[10] ~ CH[4] ~ "(-k)")) +
  scale_x_continuous(labels = 1:5) +
    coord_fixed(ratio)
    )

ggsave(here(fig_dir, 'fig2.eps'), p_response_bw, width = 88, height = 65, units = 'mm', device = cairo_ps)
# embed_fonts(here(fig_dir, 'fig2_bw.eps'))

# (p_response_gs <- ggplot(fluxes, aes(x = passage, y = log_ch4, color = treat)) +
#     stat_smooth(method = 'lm', se = FALSE, formula = 'y ~ x', linewidth = 0.5) +
#     scale_color_manual(
#       name = "Treatment", 
#       labels = c('Control', 'Selection'), 
#       values = c('gray50', 'black')) +
#     geom_jitter(#aes(alpha = selected), 
#       width = 0.1,
#       size = 0.5) + 
#         labs(x = "Passage Number", 
#                   y = expression(log[10] ~ CH[4] ~ "(-k)")) +
#   scale_x_continuous(labels = 1:5) +
#     coord_fixed(ratio)
# )
# ggsave(here(fig_dir, 'fig2_gs.png'), p_response_gs, width = 88, height = 65, units = 'mm')

@@

ratio_div <- calc_plot_ratios(divergence$passage, divergence$divergence)
(
p_div <-
ggplot(divergence, 
       aes(x = passage, 
           y = divergence)) +
    # stat_smooth(method = 'lm', 
    #             se = FALSE, 
    #             formula = 'y ~ x',
    #             color = "black",
    #             linewidth = 0.5) +
        geom_line() +
    geom_point() + 
    labs(x = expression(atop("Passage Number", " ")), 
         y = expression(atop("Divergence", log[10] ~ CH[4] ~ "(-k)"))) +
    coord_fixed(ratio_div) +
    scale_x_continuous(labels = 1:5) + 
    scale_y_continuous(n.breaks = 4) +
    theme(plot.margin = margin(0, 0.25, 0, 0.5, "cm"))
)
ratio_rh <- calc_plot_ratios(rh$sd_csum, rh$divergence)

(
p_rh <-
rh %>% 
ggplot(aes(x = sd_csum, 
           y = divergence)) +
    stat_smooth(method = 'lm',
                se = F,
                formula = 'y ~ x',
                color = "black",
                linewidth = 0.5) +
    geom_point(size = 1) + 
    labs(x = expression(atop("Cumulative Selection Differential", log[10] ~ CH[4] ~ "(-k)")), 
         y = expression(atop("Divergence", log[10] ~ CH[4] ~ "(-k)"))) +
    scale_y_continuous(n.breaks = 4) +
    # theme(plot.margin = margin(0, 0.5, 0, 0.25, "cm")) +
    coord_fixed()
)

@@

# ggsave(here(fig_dir, "fig3.png"), width = 8*.9, height = 4*.9)
# ggsave(here(fig_dir, "fig3.svg"), width = 8*.9, height = 4*.9)
ggsave(here(fig_dir, "fig3.eps"),
       p_rh,
       width = 88,
       height = 45, 
       units = 'mm',
       device = cairo_ps)
# ggsave(here(fig_dir, "fig3.eps"), 
#        p_rh,
#        width = 5,
#        height = 2.5)
# save(rh_model, file = here(der_dir, 'herit_model.RData'))

@@

centroids <-
  nmds_data %>% 
  group_by(passage, treat) %>% 
  summarize(NMDS1 = mean(NMDS1),
            NMDS2 = mean(NMDS2),
            .groups = "drop")
# p_beta_cl <-
#   nmds_data %>%   
#   ggplot(aes(x = NMDS1, y = NMDS2, shape = passage, color = treat)) +
#   geom_point() +
#   stat_ellipse(show.legend = FALSE) +
#   coord_fixed() +
#   scale_shape_discrete(name = "Passage", labels = c(2, 5)) +
#   scale_color_manual(name = "Treatment",
#                        labels = c('Control', 'Selection'),
#                        values = c('gray40', 'darkorange2')) #+
  # theme_bw() +
  # theme(
  #   plot.background = element_blank(),
  #   panel.grid.major = element_blank(),
  #   panel.grid.minor = element_blank())
  #   
# pcoa <- cmdscale(rare_dist_bray, eig = TRUE, add = TRUE)
# round(pcoa$eig*100/sum(pcoa$eig),1)
# pcoa_per_exp <- 100 * eigenvals(pcoa) / sum(eigenvals(pcoa))
# 
# ratio = pcoa_per_exp[2]/pcoa_per_exp[1]
# 
# pcoa_scores <-
#   scores(pcoa, display = "sites") %>%
#   as_tibble(rownames = "sample")
# 
# pcoa_data <-
#   aes_data %>%
#   select(sample, passage, treat) %>%
#   distinct %>%
#   inner_join(pcoa_scores, by = "sample")
# 
# # p_beta <-
#   pcoa_data %>%
#   ggplot(aes(x = Dim1, y = Dim2, shape = passage, color = treat)) +
#   geom_point() +
#   stat_ellipse(show.legend = FALSE) +
#   coord_fixed(ratio) +
#   scale_shape_discrete(name = "Passage", labels = c(2, 5)) +
#   scale_color_manual(name = "Treatment",
#                        labels = c('Neutral', 'Positive'),
#                        values = c('gray40', 'darkorange2')) #+
  # theme_bw() +
  # theme(
  #   plot.background = element_blank(),
  #   panel.grid.major = element_blank(),
  #   panel.grid.minor = element_blank())

@@

# ggsave(here(fig_dir, 'fig4.png'), p_beta, height = 2.5, width = 4) 
# ggsave(here(fig_dir, 'fig4.svg'), p_beta, height = 2.5, width = 4) 
# ggsave(here(fig_dir, 'fig4_cl.png'), p_beta_cl, height = 2.5, width = 4)

(p_beta_bw <-
  nmds_data %>%   
  ggplot(aes(x = NMDS1, y = NMDS2, shape = passage, fill = treat, 
             # linetype = treat
             )) +
  geom_point() +
  # stat_ellipse(
  #     # show.legend = FALSE
  #     ) +
  #   scale_linetype_manual(
  #     name = "Treatment", 
  #     labels = c('Control', 'Selection'), 
  #     values = c(3, 1)) +
  coord_fixed() +
  scale_shape_manual(name = "Passage", 
                     labels = c(2, 5),
                     values = c(24, 21)) +
  scale_fill_manual(name = "Treatment",
                       labels = c('Control', 'Selection'),
                       values = c('white', 'black')) +
  guides(fill=guide_legend(override.aes = list(shape=21)))
  # scale_color_manual(name = "Treatment",
  #                      labels = c('Neutral', 'Positive'),
  #                      values = c('white', 'black')) #+
  # theme_bw() +
  # theme(
  #   plot.background = element_blank(),
  #   panel.grid.major = element_blank(),
  #   panel.grid.minor = element_blank())
  #   
)
ggsave(here(fig_dir, 'fig4.eps'), 
       p_beta_bw, 
       height = 60,
       width = 180,
       # height = 60,
       # width = 88,
       units = 'mm', 
       device = cairo_ps
       )

# (p_beta_gs <-
#   nmds_data %>%   
#   ggplot(aes(x = NMDS1, y = NMDS2, shape = passage, color = treat)) +
#   geom_point() +
#   # stat_ellipse(
#   #     # show.legend = FALSE
#   #     ) +
#   coord_fixed() +
#   scale_shape_manual(name = "Passage",
#                      labels = c(2, 5),
#                      values = c(17, 19)) +
#   scale_color_manual(name = "Treatment",
#                        labels = c('Control', 'Selection'),
#                        values = c('gray50', 'black')) +
#   guides(fill=guide_legend(override.aes = list(shape=21)))
# )
# ggsave(here(fig_dir, 'fig4_gs.png'), p_beta_gs, height = 2.5*1.5, width = 4*1.5)

@@

all_taxa$Family <- factor(all_taxa$Family, levels = sort_order$Family)
all_iqm$Family <- factor(all_iqm$Family, levels = sort_order$Family)
all_taxa <-
  all_taxa %>% 
  mutate(direction = if_else(effect > 0, 0, 1))
all_iqm <-
all_taxa %>% 
  select(Family, direction) %>% 
  distinct() %>% 
  full_join(all_iqm, by = "Family")
# (p_log10_cl <-
# 	all_taxa %>%
# 	ggplot(aes(x = rel_abund, y = Family, color = treat)) +
# 	geom_point(position=position_jitterdodge()) +
# 	geom_pointrange(aes(x = median, xmax = third_quartile, xmin = first_quartile, fill = treat), 
# 			data = all_iqm, 
# 			position = position_dodge(width = 0.75), 
# 			shape = 21, 
# 			color = "black") +
# 	theme_bw() +
# 	theme(axis.text.y = element_markdown()) +
# 	labs(x = "Relative Abundance (%)", y = NULL) +
# 	scale_color_manual(name = "Treatment",
# 			   labels = c('Control', 'Selection'),
# 			   values = c('gray40', 'darkorange2')) +
# 	scale_fill_manual(name = "Treatment",
# 			   labels = c('Control', 'Selection'),
# 			   values = c('gray40', 'darkorange2')) +
#     facet_grid(direction ~ ., scale = "free_y", space = "free")  + 
# theme(
#   strip.background = element_blank(),
#   strip.text.y = element_blank()
# ) +
# 	scale_x_log10(breaks = c(0.001, 0.01, 0.1, 1),
# 		      labels = c(0.001, 0.01, 0.1, 1)))

@@

# ggsave(here(fig_dir, 'fig5.jpg'), p_log10, width = 5, height = 5)
# ggsave(here(fig_dir, 'fig5.svg'), p_log10, width = 5, height = 5)
# ggsave(here(fig_dir, 'fig5_cl.png'), p_log10_cl, width = 5, height = 5)
(p_log10_bw <-
	all_taxa %>%
	ggplot(aes(x = rel_abund, y = Family, fill = treat)) +
	geom_point(position=position_jitterdodge(jitter.width = 0.1,
	                                         dodge.width = 0.4), shape = 21, size = 1) +
        theme_bw(base_size = 7) +
            theme(panel.border = element_rect(fill = NA, linewidth = 1.0625),
                  axis.line = element_blank(),
                  text = element_text(family = 'Arial')) +
	# geom_jitter(shape = 21, height = 0.1) +
	# geom_pointrange(aes(x = median, xmax = third_quartile, xmin = first_quartile, color = treat), 
	# 		data = all_iqm, 
	# 		position = position_dodge(width = 0.75), 
	# 		shape = 21, 
	# 		# color = "black"
	# 		) +
	# theme_bw() +
	theme(axis.text.y = element_markdown()) +
	labs(x = "Relative Abundance (%)", y = NULL) +
	# scale_color_manual(name = "Treatment",
	# 		   labels = c('Control', 'Selection'),
	# 		   values = c('black', 'gray')) +
	scale_fill_manual(name = "Treatment",
			   labels = c('Control', 'Selection'),
			   values = c('white', 'black')) +
    facet_grid(direction ~ ., 
               scale = "free_y",
               space = "free")  + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank()) +
	scale_x_log10(breaks = c(0.001, 0.01, 0.1, 1),
		      labels = c(0.001, 0.01, 0.1, 1))
    )
ggsave(here(fig_dir, 'fig5.eps'), 
       p_log10_bw, 
       width = 100, 
       height = 88,
       units = 'mm',
       device = cairo_ps
       )

# (p_log10_gs <-
# 	all_taxa %>%
# 	ggplot(aes(x = rel_abund, y = Family, color = treat)) +
# 	# geom_point(position=position_jitterdodge(), shape = 21) +
# 	geom_jitter(#shape = 21, 
# 	            height = 0.1) +
# 	# geom_pointrange(aes(x = median, xmax = third_quartile, xmin = first_quartile, color = treat), 
# 	# 		data = all_iqm, 
# 	# 		position = position_dodge(width = 0.75), 
# 	# 		shape = 21, 
# 	# 		# color = "black"
# 	# 		) +
# 	theme_bw() +
# 	theme(axis.text.y = element_markdown()) +
# 	labs(x = "Relative Abundance (%)", y = NULL) +
# 	# scale_color_manual(name = "Treatment",
# 	# 		   labels = c('Control', 'Selection'),
# 	# 		   values = c('black', 'gray')) +
# 	scale_color_manual(name = "Treatment",
# 			   labels = c('Control', 'Selection'),
# 			   values = c('gray50', 'black')) +
#     facet_grid(direction ~ ., scale = "free_y", space = "free")  + 
# theme(
#   strip.background = element_blank(),
#   strip.text.y = element_blank()
# ) +
# 	scale_x_log10(breaks = c(0.001, 0.01, 0.1, 1),
# 		      labels = c(0.001, 0.01, 0.1, 1)))
# ggsave(here(fig_dir, 'fig5_gs.eps'), p_log10_gs, width = 5, height = 5)

@@

(p_effect <-
	all_taxa %>%
	ggplot(aes(x = effect, y = Family)) +
	geom_point() +

	theme_bw() +
	theme(axis.text.y = element_markdown()) +
	labs(x = "Aldex2 Effect Size", y = NULL) +
	scale_color_manual(name = "Treatment",
			   labels = c('Control', 'Selection'),
			   values = c('gray40', 'darkorange2')) +
	scale_fill_manual(name = "Treatment",
			   labels = c('Control', 'Selection'),
			   values = c('gray40', 'darkorange2'))
    )

@@

# save(p_response, herit_plot, p_beta, p_log10, file = here(der_dir, 'plots.RData'))
save(response_model, compare_response_mods, per_slope, rh_model, kt, wt, rare_median, s5, min_seqs, tidy_permanova, dbrda_aov, dbrda_percent_explained, da_fams, file = here(der_dir, 'models.RData'))
